Towards Transparency and Open Science

### 2023-02-17 manuscript.Rmd
add easteregg

I used several digital aids to improve the writing (not the content), including grammerly.com, deepl.com, and mentor.duden.de.
Also, to aid with the clarity of the writing, I asked Andreas Brandmaier, Carli Ochs, Leo Richter, Leonie Haggitte, and Caroline Gahrmann for feedback.
Furthermore, I asked Leo Richter and Maximilian Ernst for help with mathematical notation and typesetting.
Julia Delius has kindly agreed to proofread the journal articles at the time of submission and the synopsis of the thesis.
All the errors that remain are solely my responsibility.
I also prompted `ChatGPT` to write a song about reproducibility; while it was amusing, it was not funny enough to make an appearance in the text.

>>>>

I used several digital aids to improve the writing (not the content), including grammerly.com, deepl.com, and mentor.duden.de.
Also, to aid with the clarity of the writing, I asked Andreas Brandmaier, Carli Ochs, Leo Richter, Leonie Haggitte, and Caroline Gahrmann for feedback.
Furthermore, I asked Leo Richter and Maximilian Ernst for help with mathematical notation and typesetting.
Julia Delius has kindly agreed to proofread the journal articles at the time of submission and the synopsis of the thesis.
All the errors that remain are solely my responsibility.
[I also prompted `ChatGPT` to write a song about reproducibility; while it was amusing, it was not funny enough to make an appearance in the text](https://github.com/aaronpeikert/repro-talk/blob/master/gpt-songs.md).
